COG-ED Manuscript

### 2022-01-12 06_Paper/COG-ED/Manuscript.Rmd
removed leading zeros in p-value column table_2
added two headers to table_2

  #create table
  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
                             round(m1_h2c.ss$slopes[c(2:5)], digits = 2),
                             round(m1_h2c.ss$slopes[7], digits = 3),
                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI - lower", "95% CI - higher", "$p$-value", "Beta", "$SE$" )
  # columns 2:5 belong to "Slopes of NFC"
  # columns 6:7 belong to "Conditional Intercept"

@@

  table_2 <-
    kbl(h2c_ss.table,
    caption = "Interaction between NFC and n-back load level.",
    # "Slopes of n-back level for different NFC values."
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",7))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote

>>>>

  #create table
  h2c_ss.table <- data.frame("Value of NFC" = c("- 1 SD", "Mean", "+ 1 SD"),
                             round(m1_h2c.ss$slopes[c(2:3)], digits = 2),
                             c(paste0("[", round(m1_h2c.ss$slopes[1,4], digits = 2), ",", round(m1_h2c.ss$slopes[1,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[2,4], digits = 2), ",", round(m1_h2c.ss$slopes[2,5], digits = 2), "]"),
                               paste0("[", round(m1_h2c.ss$slopes[3,4], digits = 2), ",", round(m1_h2c.ss$slopes[3,5], digits = 2), "]")),
                             round(m1_h2c.ss$slopes[7], digits = 3),
                             round(m1_h2c.ss$ints[c(2,3)], digits = 2))
  colnames(h2c_ss.table) <- c("Value of NFC", "Beta", "$SE$", "95% CI", "$p$-value", "Beta", "$SE$" )
  # columns 2:5 belong to "Slopes of NFC"
  # columns 6:7 belong to "Conditional Intercept"

@@

  # remove leading zeros in the p-value column

  h2c_ss.table$`$p$-value` <- str_replace(h2c_ss.table$`$p$-value`, "0.", ".")

  table_2 <-
    kbl(h2c_ss.table,
    caption = "Interaction between NFC and n-back load level.",
    # "Slopes of n-back level for different NFC values."
    booktabs = T,                          # no vertical lines
    escape = F,                            # correctly print special characters)
    align = c("l",rep("r",6))) %>%         # right aligns the text in every numerical column
    kable_styling(latex_options = c("striped")) %>%
    add_header_above(c(" " = 1, "Slopes of NFC" = 4, "Conditional Intercept" = 2)) %>%
    footnote(general = "NFC = Need for Cognition, SE = standard error. ***$p$ < .001, **$p$ < .01, *$p$ < 0.5.",
            escape = F,                    # correctly print special characters
            threeparttable = T)            # line breaks in the footnote
